Enter our title here

### 2017-10-17 manuscript.tex
updated with figure labels
modified manuscript

1) should i add more about how it can be used in a flipped classroom

2) should i add that the courses are written in Hadley Wickham style?
  - yes one sentence

3) were you going to set something up on here that i was going to fill in? Oh the R code boxes where I can add the DataCamp edit code

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education (**do i need to cite this**). By integrating the
capabilities of technology in introductory statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.

The goal for any introductory statistics course is to help students develope the ability to think statistically
\cite{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \cite{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \cite{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\cite{Baumer2014}. While Rsoftware provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including swirl (**need to cite this?
if so what should i cite**), LearnR and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
lesson to fit the curriculum and assign it to students \cite{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

*I'm confused about LearnR and think someone else should write about it.*

@@

TryR (Code School 2014) is a web-based program and does not have swirls reproducible capability. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
introductory statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \cite{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

@@

DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized 'Premium' classes that you need to purchase. 
However, when used for academic purposes the premium DataCamp content is also free of charge.. (i'll come back to this).
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign pre-existing 
\textit{community} courses or assign a course that they've created for the particular class.

The collection of community courses avaiable at DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
\textit{Quantitative Risk Management in R} so novice through advanced programming students will benefit.
DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (cite datacamp/teach website?). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.

Each chapter in a DataCamp course is made up of modular exercises. Modulariy is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
\cite{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. If the student completes the exercise without
any help they will recieve the full points. If they ask for a hint, 30 percent of the available points will be deducted and
all of the points will be deducted if they ask for the entire answer. When in a classroom group, students can view their
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
for an exercise it will motivate them to meet their personal achievement goals. \citep{Chang2016}.

@@

\subsection{Pre-existing R courses}
DataCamp has a range of available courses that educators can use as supplimental R practice. In order to utilize 
DataCamp's \textit{classroom} benefits, you will first need to create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, you can add students by their university
email address on the \textit{Members} tab and link the account to your LMS.

\subsection{Creating a DataCamp Course}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the templete course files from the 'Create
DataCamp Course' dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
make through DataCamp will update the GitHub repository and visa versa. Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
on GitHub and under 'Settings' you can select the 'Collabroators' tab and enter the usernames of people you want to collaborate with.

The GitHub repository will contain three files: \texttt{README.md}, \texttt{course.yml}, and \texttt{chapter1.Rmd}.
\texttt{Readme.md} contains helpful information of how to get started, citing resourses to learn more about the process.
\texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
difficulty level, ect.
\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
\texttt{chapter3.Rmd}, ect.

@@

A 'NormalExercise' is an interactive coding exercise containing a lesson section, instructions, pre-exercise code, sample
code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
mode) only includes the lesson, Instructions, R script panel and a R console panel.

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{Verbatim}
\end{figure}

>>>>

It is no suprise that technology plays a vital role in practicing statistics and as the technological revolution continues to
unfold, the use of statistical software has become increasingly emphasized in education \citep{AmericanStatisticalAssociation2016}. By integrating the
capabilities of technology in statistics courses, students can explore fundamental concepts by analyzing and
interpreting real data sets \citep{Chance2007, Hardin2015, Horton2014}, giving them an authentic view of how statistics is practiced outside of the
classroom \citep{Wang2017}. The revised 2016 \textit{Guidelines for Assessment and Instruction in Statistics Education}
(GAISE) College Report has also prompted the use of more technology in introductory statistics courses, encouraging educators
to use technology "as a way to explore conceptual ideas and enhance student learning" \citep{AmericanStatisticalAssociation2016}.

The goal for any statistics course is to help students develop the ability to think statistically
\citep{AmericanStatisticalAssociation2016}.
Introducing technology into the curriculum can greatly strengthen this ability by illustrating statistical concepts such as
variability, randomness and hypothesis testing. Although numerous statistical technologies exist, R and R Studio
provide extensive statistical capabilites (free of charge) and are commonly used in statistics courses \citep{Chance2007}. R
allows students to explore real-world data sets which can not only enhance their understanding of concepts, but can also spark
an interest in the domain of statistics \citep{Wang2017}.

With this increased use of R in classrooms, there is a need for an effective way to get students familiar with statistical software
\citep{Baumer2014}. While R software provides users with extraordinary abilities there is no doubt a steep learning curve. To facilitate
this transition to R programming, popular interactive teaching technologies have been created including swirl (** need to cite package**), LearnR and TryR. 
These tools allow students to work through coding problems while recieving immediate feedback in and out of the classroom. swirl is an
open source R software package that allows students to learn R programing in their R console. This interactive learning tool
contains several pre-existing lessons but what makes swirl so popular is its versitality; educators can also create their own
lesson to fit the curriculum and assign it to students \citep{Carchedi2014}.
While swirl can be linked to a Massive Open Online Courses (MOOCs) like Coursera through API, integration of learning management 
systems (LMS) is not available for the classroom.

\textbf{Learn R section}

@@

TryR (Code School 2014) is a web-based program but is not open source. Since public content authoring
is not available, educators are limited on what they can teach their students. The R console can be intimidating to
new statistics students so an advantage of a web-based teaching tool is
the clean and easy to use interface. This is an important quality given that a lot of the time students struggle more with
software than the statistical concepts themselves \citep{Hare2017}. When students only need their web browser to participate,
all installation complications are avoided and valuable class time can be focused on the statistics, not computer issues.

@@

DataCamp has the same reproducable capabilities as swirl but is a web-based application; educators can
create their own courses that coincide with their lessons and students can access the course without having to install R.
Courses are available through the DataCamp website and students can access the lesson through their web-browser on a laptop,
tablet or moble device, making the courses accessable to anyone with an internet connection. 
The DataCamp website offers pre-existing free community courses as well as specialized \textit{Premium} classes that you need to purchase. 
However, when used for academic purposes the \textit{Premium} DataCamp content is also free for up to six months.
Any college educator can create a classroom group on the DataCamp website, add student's to the group, assign 
\textit{community} courses, \textit{Premium} courses, and even a course that they've developed themselves. 
The collection of \textit{community} courses available on DataCamp inlcude a wide range of topics from \textit{Introduction to R} to
\textit{Quantitative Risk Management in R} so novice through advanced programming students benefit.

DataCamp can be used in the classroom in a number of ways: as traditional homework assignments, as an
activity during lab periods, as pre-class assignments for a flipped classroom, and even as a test or assessment tool.

A feature that sets DataCamp apart from competing technologies is the ability to track student progress. Educators
can set deadlines for assignments and easily see not only when students complete an assignment but also which sections the
students had trouble with in a detailed report (need to cite teach page of website). Student scores can be automatically updated to a
current gradebook when you link the schools' learning management system (LMS) to DataCamp, allowing for a smooth integration of student work.

Each chapter in a DataCamp course is made up of modular exercises. Modularity is critical component in designing a statistical
learning tool because it allows independent pieces to be easily added, modified or removed from the entire functionality
\citep{Hare2017}. Course exercises can be added, modified, or deleted as new topics arise and instructors can tailor
these exercises to meet the needs of a particular class. The only disadvantage of the modularity feature is that the sessions
are not cummulative; every exercise begins with a clear workspace so an object defined in a previous exercise needs to be
defined again. Each of these exercises can be given a number of redeemable points which the students can see when they begin
the exercise, introducing a gamification feature to the learning experience. If they ask for a hint, 30 percent of the available points are deducted;
all points are deducted if they ask for the solution.  If the student completes the exercise without
any help they will recieve the full points. When in a classroom group, students can view their
progress (points and chapters completed) as well as then progress of their peers. This can help students perform better
because they want to be on par with the rest of the class; furthermore, when students can see the number of available points
for an exercise it can motivate them to meet their personal achievement goals. \citep{Chang2016}.

@@

\subsection{Pre-existing R courses}
DataCamp has a range of available courses that educators can use as supplimental R practice. In order to utilize 
DataCamp's \textit{classroom} benefits, first create an academic group on the website \url{https://www.datacamp.com/groups/education}.
After your university information has been verified and the classroom account has been approved, you can add students by their university
email address on the \textit{Members} tab and link the account to your LMS.

\subsection{Creating a DataCamp Course}
To build a course on DataCamp you will first need to create a DataCamp account by visiting \url{www.datacamp.com/teach} and
a GitHub account \url{https://github.com}. The simplest way to begin building the course is to use the template course files from the 
\texttt{Create DataCamp Course} dialog. This will automatically create a GitHub repository that is linked to DataCamp; any changes that are
make through DataCamp will update the GitHub repository and vice versa. Every DataCamp course is linked through GitHub version control,
allowing statistics educators to easily collaborate and reproduce code. To add collaborators to the course, go to the course repository
on GitHub and under \texttt{Settings} you can select the \texttt{Collabroators} tab and enter the user names of collaborators.

Newly created GitHub repositories will contain three files:

1) \texttt{README.md}

2) \texttt{course.yml}

3) \texttt{chapter1.Rmd}

\texttt{Readme.md} contains helpful information of how to get started, citing resourses to learn more about the process.
\texttt{course.yml} is a file that contains general information about the course you're creating: title, university, description,
difficulty level, ect.
\texttt{chapter1.Rmd} is a template chapter file with examples of 'normal' interative coding exercises and multiple choice questions.
To add more chapters to an R course, create new files in the repository and name them \texttt{chapter1.Rmd}, \texttt{chapter2.Rmd},
\texttt{chapter3.Rmd}, ect.

@@

A 'NormalExercise' is an interactive coding exercise containing a lesson section, instructions, pre-exercise code, sample
code, hint, solution and a submission correctness testing coded (SCT). However, the interface for students (or the 'Preview
mode) only includes the lesson, Instructions, R script panel and a R console panel (Figure~\ref{fig:code1}).

@@

msg_bad <- "That is not correct"
msg_success <- "Exactly! R can do all of these things."
test_mc(correct = 4, feedback_msgs = c(msg_bad, msg_bad, msg_bad, msg_success))
```
\end{Verbatim}
\label{fig:code1}
\end{figure}
